### 2013-09-09 research/paper/results/results-2.3.tex
uploaded 4.22 pm

 The data presented in \ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).  This further emphasizes that the galloping system is not frequency dependent. It is possible to obtain a different similar power output at different values of \usta when the damping constant \hilight{...}, is kept fixed. An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disragard the high frequencies due to shedding. As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.

@@

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output powe when the reduced velocity is increased. The key regions consists of region 1 where the $P_m$ increases with \ustar, region 2 where $P_m$ becomes maximum and region 3 where $P_m$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3.Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative. Maximum amount of power could be transferred within the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.

@@

 At region 1 where $U^*=90$ (region 1) the damping constant is high and therefore a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ Fig. \ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$. Hence both $P_d$ and $P_t$ becomes sinusoidal. However, due to the higher damping  $\theta$ does not go to the region which produces the peak power.

At region 2 ($U^*=165$) the mean power output is at its maximum. $P_t$ is not a pure sinusoidal signal. However, the  signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)). In this case at certain point in time $\theta$ arrives at the region where $F_y$ decreases but does not become negative when the angle is increased. Therefore, the force $F_y$ and $P_t$ reduces as the velocity further increased. This is because $\theta = tan^{-1}(\frac{\dot{y}}{U})$ and $\theta$ is proportional to  transverse velocity. As the velocity $\dot{y}$ is sinusoidal, $\theta$ recovers back and this leads to two `peaks'  in a single half cycle.

 At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive. As the force opposes the direction of travel, the power becomes negative. On the other hand from an energy perspective we could see that the mechanical damping is not sufficient to dissipate out the energy transferred from the fluid to the structure (as `$c$' is substantially low), therefore  part of this energy is transferred back to the fluid which is depicted as a negative power region in Fig.\ref{fig:power_time_histories} (c).

>>>>

 The data presented in \ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).  This further emphasizes that the galloping system is not frequency dependent. It is possible to obtain a different similar power output at different values of \ustar when the damping constant \hilight{...}, is kept fixed. An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disragard the high frequencies due to shedding. As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.

@@

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output powe when the reduced velocity is increased. The key regions consists of region 1 where the $P_m$ increases with \ustar, region 2 where $P_m$ becomes maximum and region 3 where $P_m$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3.Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative. Maximum amount of power could be transferred within the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.

@@

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig. \ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic foce increases with the incident angle (i.e. $0<\theta \leq < 4^0$ in \ref{fig:lift_curves}) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at lwo incident angles.

  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive. The high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $c\rho\mathcal{A}U$ is substantially low. Therefore this excess energy is trasnferred back to the fluid as depicted by the negative region of $P_d$ in \ref{fig:power_time_histories} (c)

At region 2 ($U^*=165$) the mean power output is at its maximum. $P_t$ is not a pure sinusoidal signal. However, the  signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)). In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e. $\theta=4^0$ in \ref{cy ploynomial} (a)). The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity.
